Quality Assesment of OpenStreetMap Footpath Data for 3D City Modelling

### 2020-05-09 report/report.tex
Add note about ArcGIS and Esri

Procedural city-generation models combine architectural elemets, such as streets, lots, buildings, building facades.
Urban design practises with conventional two-dimenstional deliverables range from delivering neighbourhood designs, urban zoning and building plans, to writing design codes and building ordinances.
The last decade has seen multiple startups in the area of software that aid urban arcitecture. The software uses procedural models to render a city grid based on real-world locations, or generate new user-specified parameters, and allow for varying degrees of manual editing on grid, road, neighbourhood, city block or individual feature level.
Some of the most prominent examples are CityEngine (made by the startup Procedural, bought by ESRI), Urban Canvas (made by the startup Synthicity, bought by Autodesk, now defunct) and ArcGIS (***) %TODO.

>>>>

Procedural city-generation models combine architectural elemets, such as streets, lots, buildings, building facades.
Urban design practises with conventional two-dimenstional deliverables range from delivering neighbourhood designs, urban zoning and building plans, to writing design codes and building ordinances.
The last decade has seen multiple startups in the area of software that aid urban arcitecture. The software uses procedural models to render a city grid based on real-world locations, or generate new user-specified parameters, and allow for varying degrees of manual editing on grid, road, neighbourhood, city block or individual feature level.
Some of the most prominent examples are ArcGIS Pro (made by Esri), CityEngine (made by the startup Procedural, bought by ESRI) and Urban Canvas (made by the startup Synthicity, bought by Autodesk, now defunct).
